\documentclass[12pt,a4paper]{article}

%-------------------------------------------------------
% Packages
%-------------------------------------------------------
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}

\onehalfspacing

%-------------------------------------------------------
% Hyperlinks
%-------------------------------------------------------
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

%-------------------------------------------------------
% Header & Footer
%-------------------------------------------------------
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Computer Science Portfolio Report}
\fancyhead[R]{Tahasin Ahamad}
\fancyfoot[C]{\thepage}

%-------------------------------------------------------
% Section Style
%-------------------------------------------------------
\titleformat{\section}
{\Large\bfseries}
{\thesection.}{0.5em}{}

\titleformat{\subsection}
{\large\bfseries}
{\thesubsection}{0.5em}{}

%-------------------------------------------------------
% Document
%-------------------------------------------------------

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title Page
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{titlepage}

\centering

\vspace*{1.5cm}

{\Huge\textbf{Computer Science Portfolio Report}}

\vspace{0.5cm}

{\Large Computer Science Lab}

\vspace{2cm}

\rule{0.8\textwidth}{1pt}

\vspace{1cm}

\renewcommand{\arraystretch}{1.8}

\begin{tabular}{rl}
\textbf{Student Name:} & Tahasin Ahamad \\
\textbf{Student ID:} & GH1042067 \\
\textbf{Programme:} & BSc Computer Science \\
\textbf{Module:} & B201A Computer Science Lab \\
\textbf{University:} & GISMA University of Applied Sciences \\
\textbf{Submission Date:} & 26 June 2026 \\
\end{tabular}

\vfill

\rule{0.8\textwidth}{1pt}

\vspace{0.5cm}

\Large Portfolio Website and Technical Artefacts

\end{titlepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\tableofcontents

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This report presents the development of my personal Computer Science Portfolio created for the B201A Computer Science Lab module. The portfolio showcases my technical skills, programming projects, GitHub repository, curriculum vitae (CV), and academic achievements.

The portfolio has been designed to provide a professional online presence while demonstrating practical knowledge of software development, version control, and web technologies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Portfolio Website}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The portfolio website was developed using HTML, CSS and JavaScript and is hosted using GitHub Pages.

The website contains the following sections:

\begin{itemize}
\item Home
\item About Me
\item Skills
\item Technical Artefacts
\item Education
\item Contact
\item Curriculum Vitae (CV)
\end{itemize}

The layout follows a clean and responsive design, allowing users to access the website from desktop and mobile devices.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{GitHub Repository}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The GitHub repository stores all source files related to the portfolio, including the website, technical artefacts, CV and report.

\textbf{GitHub Repository}

\url{https://github.com/tahasin71/My-Portfolio}

\vspace{0.3cm}

\textbf{Portfolio Website}

\url{https://tahasin71.github.io/My-Portfolio}

\vspace{0.3cm}

The repository is organised into folders to improve readability and simplify future development.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Technical Artefacts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Python Algorithms}

The Python Algorithms project demonstrates my understanding of algorithm design using Python.

Currently implemented:

\begin{itemize}
\item Bubble Sort
\end{itemize}

Future versions of this project will include:

\begin{itemize}
\item Binary Search
\item Linear Search
\item Selection Sort
\item Insertion Sort
\end{itemize}

The project demonstrates my understanding of loops, functions, lists and algorithm implementation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Technologies Used}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The following technologies were used during the development of this portfolio:

\begin{itemize}
\item HTML5
\item CSS3
\item JavaScript
\item Python
\item Git
\item GitHub
\item GitHub Pages
\item LaTeX
\item Visual Studio Code
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Reflection}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Throughout this project I improved my understanding of GitHub, web development, Python programming and LaTeX. I also learned how to organise software projects using Git and present technical work in a professional format.

\subsection{Strengths}

\begin{itemize}
\item Responsive portfolio website
\item Well-organised GitHub repository
\item Clean user interface
\item Professional documentation
\item Demonstrates programming skills
\end{itemize}

\subsection{Limitations}

\begin{itemize}
\item Limited number of technical artefacts at the current stage
\item Additional projects can strengthen the portfolio
\item More interactive website features could be added
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Future Improvements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Future work will include expanding the Python Algorithms collection, adding networking and cybersecurity projects, improving website accessibility and including more advanced software development projects.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Computer Science portfolio provides a professional overview of my academic progress, technical skills and programming experience. It demonstrates my ability to develop software, organise projects using GitHub and present technical work in a structured and professional manner.

\end{document}
